Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-18 report/report.tex
Newlines for algorithm comments, ensure x is a vector everywhere

\begin{algorithm}[H]
\SetAlgoLined
\KwResult{Write here the result }
    // Find the point with the maximum distance\;
    $d_{max}$ = 0\;
    $index$ = 0\;
    $end$ = length(PointList)\;

@@

    // If max distance is greater than epsilon, recursively simplify\;
    \eIf{$d_{max}$ $>$ $\epsilon$} {
        // Recursive call\;
        recResults1[] = Douglas-Peucker(PointList[1...$index$], $\epsilon$)\;
        recResults2[] = Douglas-Peucker(PointList[$index$...$end$], $\epsilon$)\;

        // Build the result list\;
        ResultList[] = {recResults1[1...length(recResults1) - 1], recResults2[1...length(recResults2)]}\;
    }{
        ResultList[] = {PointList[1], PointList[$end$]}\;
    }
    \Return{ResultList[]}\;

@@

>>>>

\begin{algorithm}[H]
\SetAlgoLined
\KwResult{Write here the result }
    \textbf{Input:} PointList\\
    // Find the point with the maximum distance\\
    $d_{max}$ = 0\;
    $index$ = 0\;
    $end$ = length(PointList)\;

@@

    // If max distance is greater than epsilon, recursively simplify\\
    \eIf{$d_{max}$ $>$ $\epsilon$} {
        // Recursive call\\
        recResults1[] = Douglas-Peucker(PointList[1...$index$], $\epsilon$)\;
        recResults2[] = Douglas-Peucker(PointList[$index$...$end$], $\epsilon$)\;

        // Build the result list\\
        ResultList[] = {recResults1[1...length(recResults1) - 1], recResults2[1...length(recResults2)]}\;
    }{
        ResultList[] = {PointList[1], PointList[$end$]}\;
    }
    \Return{ResultList[]}\;

@@

\begin{algorithm}[H]
\SetAlgoLined
\KwResult{A float representing the shortests distance between $A$ and $B$}
    \textbf{Input:} Line segment $A$: [$\vec{a_1}$, $\vec{a_2}$], Line segment $B$: [$\vec{b_1}$, $\vec{b_2}$]\\
    // First assume that the points of $A$ and $B$ are ordered so that $\vec{a_1}$ is closer to $\vec{b_1}$ than to $\vec{b_2}$.\\

    // Check if the line segments $A$ and $B$ intersect, if so, the distance between them is 0.\\
    $\vec{x_s}$ = lineLineIntersection($A$, $B$)\;
    \If{$\vec{x_s}$ is not None} {
        \Return{0}
    }

    // Get the line-line intersection between the lines spanned by $A$ and $B$. Note that if an intersection exists, it must lie outside of both $A$ and $B$.\\
    $\vec{x}$ = lineLineIntersection($A$, $B$)\;

    // Case 1: No intersection. The lines are parallel.\\
    \If{$\vec{x}$ is None} {
        \Return{perpendicularLineDistance($A$, $B$)}\;
    }

    // Get the projections of $\vec{b_1}$ and $\vec{b_2}$ on the line spanned by $A$:\\
    $\vec{d_1}$ = linearProjection($\vec{b_1}$, $A$)\;
    $\vec{d_2}$ = linearProjection($\vec{b_2}$, $A$)\;

    // Case 2: The projection of $B$ onto $A$ is completely disjoint from $A$ with no common points. In this case, no perpendicular distance can be inferred.\\
    \If{$\vec{d_1}-\vec{a_1} \cdot \vec{d_1}-\vec{a_2} > 0$ or $\vec{d_2}-\vec{a_1} \cdot \vec{d_2}-\vec{a_2} > 0$} {
        \Return{None}\;
    }
    \newpage

    // Case 3: $\vec{x}$ lies between $\vec{a_1}$ and $\vec{a_2}$.\\
    \If{$\vec{x}-\vec{a_1} \cdot \vec{a_2}-\vec{x} > 0$} {
        // Project the endpoints of $B$ on $A$, to find out which endpoint is closer to the intersection\\
        $d_{pl1}$ = pointLineDistance($\vec{b_1}$, $A$)\;
        $d_{pl2}$ = pointLineDistance($\vec{b_2}$, $A$)\;
        \eIf{$d_{pl1} < d_{pl2}$} {
            \Return{$d_{pl1}$}\;
        } {
            \Return{$d_{pl2}$}\;
        }
    }

    \eIf{|$\vec{x}$-$\vec{a_1}$| < |$\vec{x}$-$\vec{a_2}$|} {
        // Case 4: $\vec{x}$ is to the left of $\vec{a_1}$\\
        $\vec{a}$ = $\vec{a_1}$\;
        $\vec{b}$ = $\vec{b_1}$\;
    } {
        // Case 5: $\vec{x}$ is to the right of $\vec{a_2}$\\
        $\vec{a}$ = $\vec{a_2}$\;
        $\vec{b}$ = $\vec{b_2}$\;
    }

    $\vec{p}$ = linearProjection($\vec{b}-\vec{x}$, $\vec{a}-\vec{x}$)\;
    \eIf{|$\vec{p}$| < |$\vec{a}$-$\vec{x}$|} {
        $\vec{k}$ = $\vec{d}$\;
    } {
        $\vec{k}$ = $\vec{a}-\vec{x}$\;
    }

    $\theta = \arccos{|\vec{d}|/|\vec{b}-\vec{x}|}$\;
    \Return{$\tan{\theta} \cdot |\vec{k}|$}

    \caption{Projected Line Segment Distance}
\end{algorithm}
